### 2020-03-25 eca2019proceedings.tex
voorwerk

\section*{Committees}
	\addcontentsline{toc}{chapter}{Committees}
	\subsection*{General chairs}
	\begin{compactitem}[]
	\item[] Bart Verheij
	\item[] Marco Wiering
	\end{compactitem}

	\subsection*{Contact \& administration}
	\begin{compactitem}[]
	\item[] Elina Sietsema
	\item[] Carlijne de Vries
	\item[] Sarah van Wouwe
	\end{compactitem}

	\subsection*{Local organisation}
	\begin{compactitem}[]
		\item[] Luca Bandelli
		\item[] Abe Brandsma
		\item[] Tomasz Darmetko
		\item[] Mingcheng Ding
		\item[] Ana Dugeniuc
		\item[] Joel During
		\item[] Ameer Islam
		\item[] Siebert Looije
		\item[] Ren\'e Mellema
		\item[] Michaela Mr\`azkov\'a
		\item[] Annet Onnes
		\item[] Benjamin Shafrey
		\item[] Sjaak ten Caat
		\item[] Albert Thie
		\item[] Jelmer van der Linde
		\item[] Luuk van Keeken
		\item[] Paul Veldhuyzen
		\item[] Randy Wind
		\item[] Galiya Yeshmagambetova
	\end{compactitem}

	\subsection*{Program committee}
	\begin{compactitem}[]
		\item[] Stylianos Asteriadis, Maastricht University
		\item[] Reyhan Aydogan, Delft University of Technology
		\item[] Floris Bex, Utrecht University
		\item[] Michael Biehl, University of Groningen
		\item[] Mauro Birattari, Universit\'e Libre de Bruxelles
		\item[] Hendrik Blockeel, Katholieke Universiteit Leuven
		\item[] Hans L. Bodlaender, Utrecht University
		\item[] Sander Bohte, Centrum Wiskunde \& Informatica (CWI)
		\item[] Peter Bosman, Centrum Wiskunde \& Informatica (CWI)
		\item[] Tibor Bosse, Vrije Universiteit Amsterdam
		\item[] Bruno Bouzy, Paris Descartes University
		\item[] Frances Brazier, Delft University of Technology
		\item[] Bert Bredeweg, University of Amsterdam
		\item[] Tristan Cazenave, Universit\'e Paris Dauphine
		\item[] Tom Claassen, Radboud University Nijmegen
		\item[] Walter Daelemans, University of Antwerp
		\item[] Gregoire Danoy, University of Luxembourg
		\item[] Mehdi Dastani, Utrecht University
		\item[] Patrick De Causmaecker, Katholieke Universiteit Leuven
		\item[] Martine De Cock, University of Washington Tacoma
		\item[] Mathijs De Weerdt, Delft University of Technology
		\item[] Beno\^it Depaire, Hasselt University
		\item[] Frank Dignum, Utrecht University
		\item[] Virginia Dignum, Delft University of Technology
		\item[] Kurt Driessens, Maastricht University
		\item[] Madalina Drugan, Technical University of Eindhoven
		\item[] Sjur Dyrkolbotn, Western Norway University of Applied Sciences
		\item[] Jason Farquhar, Radboud University Nijmegen
		\item[] Ad Feelders, Utrecht University
		\item[] Bart Goethals, University of Antwerp
		\item[] Pascal Gribomont, University of Liège
		\item[] Perry Groot, Radboud University Nijmegen
		\item[] Marc Gyssens, Universiteit Hasselt
		\item[] Frank Harmsen, Ernst \& Young Advisory
		\item[] Maaike Harbers, Rotterdam University of Applied Sciences
		\item[] Tom Heskes, Radboud University Nijmegen
		\item[] Koen Hindriks, Delft University of Technology
		\item[] Arjen Hommersom, Open University of the Netherlands
		\item[] Mark Hoogendoorn, Vrije Universiteit Amsterdam
		\item[] Gerda Janssens, Katholieke Universiteit Leuven
		\item[] Maurits Kaptein, Eindhoven University of Technology
		\item[] Uzay Kaymak, Eindhoven University of Technology
		\item[] Walter Kosters, Leiden University
		\item[] Johan Kwisthout, Radboud University Nijmegen
		\item[] Tom Lenaerts, Université Libre de Bruxelles
		\item[] Marco Loog, Delft University of Technology
		\item[] Peter Lucas, Radboud University
		\item[] Elena Marchiori, Radboud University Nijmegen
		\item[] Wannes Meert, Katholieke Universiteit Leuven
		\item[] John-Jules Meyer, Utrecht University
		\item[] Peter Nov\'ak, Delft University of Technology
		\item[] Ann Now\'e, Vrije Universiteit Brussel
		\item[] Aske Plaat, Leiden University
		\item[] Eric Postma, Tilburg University
		\item[] Henry Prakken, University of Utrecht, University of Groningen
		\item[] Jan Ramon, INRIA
		\item[] Silja Renooij, Utrecht University
		\item[] Nico Roos, Maastricht University
		\item[] Stefan Schlobach, Vrije Universiteit Amsterdam
		\item[] Pierre-Yves Schobbens, University of Namur
		\item[] Johannes Scholtes, Maastricht University
		\item[] Lambert Schomaker, University of Groningen
		\item[] Martijn Schut, Universiteit van Amsterdam
		\item[] Evgueni Smirnov, Maastricht University
		\item[] Matthijs T. J. Spaan, Delft University of Technology
		\item[] Gerasimos Spanakis, Maastricht University
		\item[] Jennifer Spenader, University of Groningen
		\item[] Ida Sprinkhuizen-Kuyper, Radboud University Nijmegen
		\item[] Thomas Stützle, Universit\'e Libre de Bruxelles
		\item[] Johan Suykens, Katholieke Universiteit Leuven
		\item[] Niels Taatgen, University of Groningen
		\item[] Annette Ten Teije, Vrije Universiteit Amsterdam
		\item[] Dirk Thierens, Utrecht University
		\item[] Karl Tuyls, University of Liverpool
		\item[] Antal van den Bosch, Radboud University Nijmegen
		\item[] Egon L. van den Broek, Utrecht University
		\item[] Jaap van den Herik, Leiden University
		\item[] Linda van der Gaag, Utrecht University
		\item[] Peter van der Putten, Leiden University, Pegasystems
		\item[] Leon van der Torre, University of Luxembourg
		\item[] Natalie van der Wal, Vrije Universiteit Amsterdam
		\item[] Tim van Erven, Leiden University
		\item[] Marcel van Gerven, Radboud University Nijmegen
		\item[] Frank van Harmelen, Vrije Universiteit Amsterdam
		\item[] Martijn van Otterlo, Vrije Universiteit Amsterdam
		\item[] M. Birna van Riemsdijk, Delft University of Technology
		\item[] Maarten van Someren, University of Amsterdam
		\item[] Marieke van Vugt, University of Groningen
		\item[] Menno van Zaanen, Tilburg University
		\item[] Joaquin Vanschoren, Eindhoven University of Technology
		\item[] Marina Velikova, Radboud University Nijmegen
		\item[] Remco Veltkamp, Utrecht University
		\item[] Joost Vennekens, Katholieke Universiteit Leuven
		\item[] Katja Verbeeck, Technologiecampus Gent
		\item[] Rineke Verbrugge, University of Groningen
		\item[] Michel Verleysen, Universit\'e Catholique de Louvain
		\item[] Sicco Verwer, Delft University of Technology
		\item[] Arnoud Visser, Universiteit van Amsterdam
		\item[] Willem Waegeman, Ghent University
		\item[] Martijn Warnier, Delft University of Technology
		\item[] Gerhard Weiss, Maastricht University
		\item[] Floris Wiesman, Academic Medical Center Amsterdam
		\item[] Jef Wijsen, University of Mons
		\item[] Mark H. M. Winands, Maastricht University
		\item[] Radboud Winkels, Universiteit van Amsterdam
		\item[] Cees Witteveen, Delft University of Technology
		\item[] Marcel Worring, University of Amsterdam
		\item[] Yingqian Zhang, Eindhoven University of Technology
	\end{compactitem}

\include{preface}

>>>>

\include{prep}

### 2020-03-25 preface.tex
voorwerk

BNAIC is the annual Benelux Conference on Artificial Intelligence. In 2017, the 29\textsuperscript{th} edition of BNAIC is organized by the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), University of Groningen, under the auspices of the Benelux Association for Artificial Intelligence (BNVKI) and the Dutch Research School for Information and Knowledge Systems (SIKS).

BNAIC 2017 takes place in Het Kasteel, Melkweg 1, Groningen, The Netherlands, on Wednesday November 8 and Thursday November 9, 2017. BNAIC 2017 includes invited speakers, research presentations, posters, demonstrations, a deep learning workshop (organized by our sponsor NVIDIA) and a research and business session.

The four BNAIC 2017 keynote speakers are:

\begin{itemize}
	\item 
Marco Dorigo, Universit\'{e} Libre de Bruxelles\\
\emph{Swarm Robotics: Current Research Directions at IRIDIA}

	\item 
Laurens van der Maaten, Facebook AI Research\\
\emph{From Visual Recognition to Visual Understanding}

	\item 
Luc Steels, Institute for Advanced Studies (ICREA), Barcelona\\
\emph{Digital Replicants and Mind-Uploading
}

	\item 
Rineke Verbrugge, University of Groningen\\
\emph{Recursive Theory of Mind: Between Logic and Cognition}
\end{itemize}

\noindent Three FACt talks (FACulty focusing on the FACts of Artificial Intelligence) are scheduled:

\begin{itemize}
	\item 
Bert Bredeweg, Universiteit van Amsterdam\\
\emph{Humanly AI: Creating smart people with AI}
	\item Eric Postma, Tilburg University\\
\emph{Towards Artificial Human-like Intelligence}
	\item Geraint Wiggins, Queen Mary University of London/Vrije Universiteit Brussel\\
\emph{Introducing Computational Creativity}
\end{itemize}

\noindent Authors were invited to submit papers on all aspects of Artificial Intelligence. This year we have received 68 submissions in total. Of the 30 submitted Type A regular papers, 11 (37\%) were accepted for oral presentation, and 14 (47\%) for poster presentation. 5 (17\%) were rejected. Of the 19 submitted Type B compressed contributions, 17 (89\%) were accepted for oral presentation, and 2 (11\%) for poster presentation. None were rejected. All 6 submitted Type C demonstration abstracts were accepted. Of the submitted 13 Type D thesis abstracts, 5 (38\%) were accepted for oral presentation, and 8 (62\%) for poster presentation. None were rejected. The selection was made using peer review. Each submission was assigned to three members of the program committee, and their expert reviews were the basis for our decisions.

All submissions accepted for oral or poster presentations and all demonstration abstracts appear in the electronic preproceedings, made available on the conference web site during the conference (\url{http://bnaic2017.ai.rug.nl/}). All 11 Type A regular papers accepted for oral presentation will appear in the postproceedings, to be published in the Springer CCIS series after the conference.

The BNAIC 2017 conference would not be possible without the support and efforts of many. We thank the members of the program committee for their constructive and scholarly reviews. We are grateful to 
    Elina Sietsema, Carlijne de Vries and 
		Sarah van Wouwe, members of the administrative staff at the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), for their tireless and reliable support. We thank our local organisation team 
		Luca Bandelli,
    Abe Brandsma,
    Tomasz Darmetko,
    Mingcheng Ding,
    Ana Dugeniuc,
    Joel During,
    Ameer Islam,
    Siebert Looije,
    Ren\'{e} Mellema,
    Michaela Mr\'{a}zkov\'{a},
    Annet Onnes,
    Benjamin Shaffrey,
    Sjaak ten Caat,
    Albert Thie,
    Jelmer van der Linde,
    Luuk van Keeken,
    Paul Veldhuyzen,
    Randy Wind, and
    Galiya Yeshmagambetova, 
all students in our BSc and MSc Artificial Intelligence programs, for enthusiastically volunteering to help out in many ways. We thank Annet Onnes for preparing the preproceedings, Jelmer van der Linde for developing the web site, Randy Wind for designing the program leaflet, and Albert Thie for coordinating the local organisation.

We are grateful to our sponsors for their generous support of the conference:
\begin{itemize}
%		
	\item 
Target Holding
	\item 
NVIDIA Deep Learning Institute
%
	\item 
Anchormen
	\item 
Quint
	\item 
the Netherlands Research School for Information and Knowledge Systems (SIKS)
	\item 
SIM-CI
%
	\item 
Textkernel
	\item 
LuxAI
	\item 
IOS Press
	\item 
Stichting Knowledge-Based Systems (SKBS)
	\item 
SSN Adaptive Intelligence 
\end{itemize}

\noindent 
We wish you a pleasant conference!

\begin{flushright}
Bart Verheij \& Marco Wiering
\end{flushright}

>>>>

After two successful editions held in Lisbon in 2015 and Fribourg in 2017, ECA was hosted in 2019 by the Faculty of Philosophy of the University of Groningen, on 24-27 June 2019. These two volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.
The European Conference on Argumentation (ECA) is a pan-European biennial initiative aiming to consolidate and advance various strands of research on argumentation and reasoning by gathering scholars from a range of disciplines. While based in Europe, ECA involves and encourages participation by argumentation scholars from all over the world; it welcomes submissions linked to argumentation studies in general, in addition to those tackling the conference theme. The 2019 Groningen edition focused on dissent. The goal was to inquire into the virtues and vices of dissent, criticism, disagreement, objections, and controversy in light of legitimizing policy decisions, justifying beliefs, proving theorems, defending standpoints, or strengthening informed consent. It is well known that dissent may hinder the cooperation and reciprocity required for reason-based deliberation and decision-making. But then again, dissent also produces the kind of scrutiny and criticism required for reliable and robust outcomes. How much dissent does an argumentative practice require? What kinds of dissent should we promote, or discourage? How to deal with dissent virtuously? How to exploit dissent in artificial arguers? How has dissent been conceptualized in the history of rhetoric, dialectic and logic? The papers in these two volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).
The conference had 224 participants, and 188 papers were presented. These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation. The contents of these two volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
The proceedings contain papers that were accepted based on abstract submissions; each submission was thoroughly evaluated by three reviewers of our scientific board—for a full list of ECA committees, see www.ecargument.org. Volume I gathers ?? long papers and associated commentaries, together with ?? papers presented in the ?? thematic panels that were held during ECA2019. Volume II gathers ?? regular papers that were presented during the conference. 
Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings. First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality. In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants. Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these two volumes, and assisted us throughout in the process of producing the Proceedings.
The next edition of ECA will take place in Rome in 2021, and we look forward to seeing the ECA community gathering again for another successful event.

Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar, Bart Verheij
